
  \section{Fundamentals of Continuum Physics for Thermo-Hydrodynamical Problems}

    \begin{itemize}
        \item Cartesian Grid Components 3d
        \item Final Forms ideally integrals which are the starting point for finite volume methods
      \end{itemize}

      This section covers the set of fundamental equations for thermo-hydrodynamical problems which the numerical solution techniques of the following chapters are aiming to solve. Furthermore the notation regarding the physical quantities to be used throughout this thesis is introduced. The following paragraphs are based on (Kundu, Spurk, Ferziger, Anderson). For a thorough derivation of the matter to be presented the reader may consult the mentioned sources. Since the present thesis focusses on the application of finite-volume methods the focus lays on stating the integral forms of the relevant conservation laws. Einstein's convention for taking sums over repeated indices is used to simplify certain expressions. For the remainder of this thesis non-moving inertial frames in a Cartesian coordinate system with the coordinates \( x_i \) are used. This approach is also known as \textit{Eulerian approach}. 

    \subsection{Conservation of Mass -- Continuity Equation}

    The conservation law of mass embraces the physical concept that, neglecting relativistic and nuclear reactions, mass cannot be created or destroyed. Using the notion of a mathematical control volume, which is used to denote a constant domain of integration, one can state the integral mass balance of a control volume \(V\) with control surface \(S\) using Gauss' theorem as

    \begin{equation}
      \label{eq:contifull}
      \iiint\limits_V \frac{\partial \rho}{\partial t} + \frac{\partial}{\partial x_i}\left( \rho u_i \right) \mathrm{d}V 
      =  \iiint\limits_V \frac{\partial \rho}{\partial t} \mathrm{d}V + \iint\limits_S \rho u_i n_i \mathrm{d}S
      = 0.
    \end{equation}

    \subsection{Conservation of Momentum -- Cauchy-Equations}

    The conservation law of momentum, also known as Newton's Second Law, axiomatically demands the balance of the temporal change of momentum and the sum of all attacking forces of a body. Those forces can be divided into body forces and surface forces. Let \(k_i\) denote a mass specific force and \(t_i\) the stress vector. A first form of the integral momentum balance in the direction of \(x_i\) can be formulated as

    \begin{displaymath}
      \iiint\limits_V \frac{\partial \left(\rho u_i \right)}{\partial t} \mathrm{d}V + \iint\limits_S \rho u_i \left( u_j n_j \right) \mathrm{d}S = \iiint\limits_V \rho k_i \mathrm{d}V + \iint\limits_S t_i \mathrm{d}S.
    \end{displaymath}

    In general the stress vector \(\vec{t} = \left( t_i \right)_{i = 1, \dots, 3}\) is a function not only of the location \(\vec{x} = \left( x_i \right)_{i = 1,\dots,3}\) and of the time \(t\) but also of the normal vector \(\vec{n} = \left( n_i \right)_{i = 1,\dots,3} \). A central simplification can be introduced, namely Cauchy's stress theorem, which states that the stress vector is the image of the normal vector under a linear mapping \(\vec{T}\). With respect to the Cartesian canonical basis \(\left(\vec{e}_i \right)_{i = 1, \dots, 3}\) the mapping \(T\) is represented by the coefficient matrix \( \left(\tau_{ji}\right)_{i,j = 1,\dots,3}\) and Cauchy's stress theorem reads

    \begin{displaymath}
      \vec{t}\left(x,t,n\right) = \vec{T}(x,t,n) = \left(\tau_{ji} n_j\right)_{i = 1, \dots, 3}.
    \end{displaymath}

    Assuming the validity of Cauchy's stress theorem one can derive Cauchy's first law of motion, which in integral form can be formulated as

    \begin{equation}
      \label{eq:cauchymotion}
      \iiint\limits_V \frac{\partial \left(\rho u_i \right)}{\partial t} \mathrm{d}V + \iint\limits_S \rho u_i \left( u_j n_j \right) \mathrm{d}S = \iiint\limits_V \rho k_i \mathrm{d}V + \iint\limits_S \tau_{ji}n_j \mathrm{d}S
    \end{equation}

    and represents the starting point for the modelling of fluid mechanical problems. One should note, that Cauchy's first law of motion does not take any assumptions regarding material properties, which is why the set of equations (1,2) is not closed in the sense that there exists a independent equation for each of the dependent variables.

    %\subsection{Conservation of Angular Momentum}
    \subsection{Closing the System of Equations -- Newtonian Fluids}

    As result of Cauchy's theorem the stress vector \( \vec{t} \) can be specified once the nine components \(\tau_{ji}\) of the coefficient matrix are known. As is shown in (Spurk usw.) by formulating the conservation law of angular momentum the coefficient matrix is symmetric, 

    \begin{equation}
      \label{eq:stresssymetry}
      \tau_{ji} = \tau_{ij},
    \end{equation}
    
    hence the number of unknown coefficients reduces to six components. In a first step it is assumed that the coefficient matrix can be decomposed into fluid-static and fluid-dynamic contributions,

    \begin{displaymath}
      \tau_{ij} = -p \delta_{ij} + \sigma_{ij},
    \end{displaymath}

    where \(p\) is the thermodynamic pressure, \(\delta_{ij}\) is the \textit{Kronecker}-Delta and \( \sigma_{ij} \) is the so called \textit{deviatoric stress tensor}. For the fluids the studies that the present thesis performs it is sufficient to consider viscous fluids for which there exists a linear relation between the components of the deviatoric stress tensor and the symmetric part of the transpose of the Jacobian of the velocity field \(\left( S_{ij} \right)_{i,j=1,\dots,3}\),

    \begin{displaymath}
      S_{ij} = \frac{1}{2} \left( \left( \frac{\partial u_i}{\partial x_j} \right) + \left( \frac{\partial u_j}{\partial x_i} \right) \right).
    \end{displaymath}

    If one now imposes material-isotropy and the mentioned stress-symmetry (\ref{eq:stresssymetry}) restriction it can be shown (Aries) that the constitutive equation for the deviatoric stress tensor reads 

    \begin{displaymath}
      \sigma_{ij} = 2 \mu S_{ij} + \lambda S_{mm} \delta_{ij}
    \end{displaymath}

    where \(\lambda\) and \(\mu\) denominate scalars which depend on the local thermodynamical state. Taking everything into account (\ref{eq:cauchymotion}) can be formulated as the integral conservation law of momentum for newtonian fluids, better known as the \textit{Navier-Stokes equations} in integral form:

    \begin{equation}
      \iiint\limits_V \frac{\partial \left(\rho u_i \right)}{\partial t} \mathrm{d}V 
      + \iint\limits_S \rho u_i \left( u_j n_j \right) \mathrm{d}S 
      = \iiint\limits_V \rho k_i \mathrm{d}V 
      + \iint\limits_S -p n_i 
      + \mu \left( \left( \frac{\partial u_i}{\partial x_j} \right) + \left( \frac{\partial u_j}{\partial x_i} \right) \right) n_j 
      + \lambda \frac{\partial u_m}{\partial x_m} n_i
      \mathrm{d}S
    \end{equation}

    \subsection{Conservation Law for Scalar Quantities}

    The modelling of the transport of scalar quantities, convection, by a flow field \(\vec{u}\) is necessary if the fluid mechanical problem to be analyzed includes for example heat transfer. Other scenarios that involve the necessity to model scalar transport surge, when turbulent flows are to be modeled by two-equation models like the \(k\)-\(\varepsilon\)-model (Pope). 
    
    Since this thesis focusses on the transport of the scalar temperature \(T\) this section introduces the conservation law for energy in integral form,

    \begin{equation}
      \iiint\limits_V \frac{\partial \left(\rho T \right)}{\partial t}\mathrm{d}V + \iint\limits_S \rho u_j - \kappa \frac{\partial T}{\partial x_j} n_j \mathrm{d}S= \iiint\limits_V  q_T \mathrm{d}V,
    \end{equation}

    where \(\kappa\) denotes the thermal conductivity of the modelled material and \(q_T\) is a scalar field representing sources and sinks of heat throughout the domain of the problem. 

        %Check also Peric p12 or Bird et al. (1962).

    \subsection{Necessary Simplification of Equations}
        Negligible viscous dissipation and and pressure work source terms in the enery equation (vakilipour)

        The purpose of this section is to motivate and introduce further common simplifications of the previously presented set of constitutive equations. 

      \subsubsection{Incompressible Flows and Hydrostatic Pressure}

      A common simplification when modelling low Mach number flows (\(Ma < 0.3\)) is the assumption of \textit{incompressibility}, or the assumption of an \textit{isochoric} flow. If one furthermore assumes homogeneous density \(rho\) in space and time, a restrictive assumption that will be partially alleviated in the following section the continuity equation in integral form (\ref{eq:contifull}) can be simplified to

      \begin{equation}
        \label{eq:contiinc}
        \iint\limits_S \rho u_i n_i \mathrm{d}S = 0.
      \end{equation}

      If furthermore, one assumes also constant dynamic viscosity \(\mu\) the Navier-Stokes equations in integral form can be reduced to 

    \begin{equation}
      \iiint\limits_V \rho \frac{\partial \left( u_i \right)}{\partial t} \mathrm{d}V 
      + \iint\limits_S \rho u_i \left( u_j n_j \right) \mathrm{d}S 
      = \iiint\limits_V \rho k_i \mathrm{d}V 
      + \iint\limits_S -p n_i 
      + \mu \left( \left( \frac{\partial u_i}{\partial x_j} \right) + \left( \frac{\partial u_j}{\partial x_i} \right) \right) n_j 
      + \lambda \frac{\partial u_m}{\partial x_m} n_i 
      \mathrm{d}S
    \end{equation}
     
      by using the interchangeability of differentiation an integration and application of \(\ref{eq:contiinc}\)

      \subsubsection{Variation of Fluid Properties -- The Boussinesq Approximation}
      Talk about natural and forced convection. Differences for the solver algorithm. (s.a.) Peric P447
      Talk about flows with variation in fluid properties -> mms has to map this behaviour (Buoyancy force driven, i.e. naturally convected fluid), mixed Convection
      Also talk about non-dimensional values like Prandtl number, Rayleigh and Reynolds
    \subsection{Final Form of the Set of Equations}
        Conservative and Non-Conservative Form
